---
title: "Time Series_Quarterly Imports"
author: "Anita S George"
date: "8/27/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import file


```{r}
data<-read.csv("D:/Anita docs/MDS-3RD SEM/time series/quarterlyukimport.csv")
```

## Time Series analysis
-Convert data into ts object

-Plot ts and acf of data (to check if stationary or not)

-Identify the non stationarity components

-Test for nonstationarity(ADF Test)

-Transform the data into stationary series

-Examine the acf and pacf of stationary data

-Fit ARMA model

-Examine residuals

-make predictions

```{r}
#library(tseries)
#library(forecast)
data1=ts(data,start=c(1960,1),end=c(1970,1),frequency=4)
#attach(data$imports) #helps to extract the variable from data
ts.plot(data1,main="UK import data")#ts plot
acf(data1)
#ts plot shows that data has trend component and acf shows non random series(non stationary)
```

```{r}
#Ho=data is non stationary
adf.test(data1)

```

p-value is greater tahn 0.05, so null hypothesis is accepted(i.e it is non stationary in nature)


```{r}
#making data stationary
diffdata<-diff(data1)
ts.plot(diffdata)
acf(diffdata)
adf.test(diffdata)
```

```{r}
acf(diffdata)
pacf(diffdata)
```

MA(1) as acf cuts after lag 1 and pacf is oscillatory


```{r}
fit=auto.arima(diffdata,seasonal=FALSE)
fit
fit=auto.arima(data1,seasonal=FALSE)
fit
```


Residual analysis
```{r}
fit=auto.arima(data1,seasonal=FALSE)#to obtain residuals fit for original data
fit
res=residuals(fit)
plot(res,main="Residuals of the fitted model")
```
We have to verify if the assumptions on error term are satisfied(i.e. uncorrelated[verified using acf],iid,normally distributed with mean 0 and const variance)
```{r}
acf(res)
```
this shows it is uncorrelated

To check for normality:
Ho:it is normally distributed
```{r}
shapiro.test(res)
```

Since p-value>0.05, residual series are normally distributed as null hypothesis accepted.


Prediction(next 4 observations)
```{r}
newfit=forecast(fit,h=4)
newfit
```
Forecast-Two types: Out sample forecast and insample forecast. The above case is out of sample forecast

```{r}
plot(newfit)
```

